Excitonic Energy Transfer Couplings at Short Distances: Efficient Transfer-Integral Fragmentation Approach Based on Effective One-Electron Operators

### 2019-08-27 papers/3_eet.I.Theory/paper-r0.tex
Entire OEP-based EET model described

@@

%First, in Section II we briefly review the Fujimoto's TI/CIS model of EET coupling
%which is treated in this work as a reference.
%Then, further in this Section, we derive the OEP model based on the TI/CIS model (here referred to as the
%which is validated in Section III against the TI/CIS method for a few model complexes. 
First, in Section II we derive the OEP model based on the TI/CIS model (here referred to as the
OEP-TI/CIS model). Next, we validate it against the TI/CIS method for a few model complexes
in Section III. 
Finally, we conclude our work in Section IV.

@@

%In the above equatons, the superscript (0) denotes that the matrix elements are not affected by the
%overlap between molecular wavefunctions, and are given by
%%
%\begin{align}
% V^{{\rm Coul},(0)} &= \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
%  P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
%  (\mu\nu | \sigma\lambda) \\
% V^{{\rm Exch},(0)} &=-\frac{1}{2} \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
%  P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
%  (\mu\lambda | \sigma\nu) \\
% V^{{\rm HT1},(0)} &= t_{H\rightarrow L}^A \left\{-\big( H^A \big| \mathscr{F} \big| H^B \big) 
%   + 2 \big( H^A L^A \big| L^A H^B \big) - \big( H^A H^B \big| L^A L^A \big)  \right\} \\
% V^{{\rm HT2},(0)} &= t_{H\rightarrow L}^B \left\{-\big( H^A \big| \mathscr{F} \big| H^B \big) 
%   + 2 \big( H^A L^B \big| L^B H^B \big) - \big( H^A H^B \big| L^B L^B \big)  \right\} \\
% V^{{\rm CT },(0)} &= 
%     2 \big( H^A L^B \big| L^A H^B \big) - \big( H^A H^B \big| L^A L^B \Big) 
%\end{align}
%%
%In the above, $\mathscr{F}$ is the Fock operator whereas $H$ and $L$ denote the 
%HOMO and LUMO orbitals, respectively. It was found that the overlap corrections
%are quite negligible.

To account for the EET coupling via charge transfer states

@@

@@

@@

To summarize, the overall form of the OEP-TI/CIS model is still given as in the original TI/CIS model
by
%
\begin{equation}
  V \approx V^{\rm Direct} + V^{\rm Inirect} \;,
\end{equation}
%
where the so called `direct' and `indirect' coupling constants are respectively
%
\begin{subequations}
\begin{align}
  V^{\rm Direct  } &\equiv V^{\rm Coul} + V^{\rm Exch} + V^{\rm Ovrl} \;,\\
  V^{\rm Indirect} &\equiv V^{\rm TI-2} + V^{\rm TI-3} \;,
\end{align}
\end{subequations}
%
with
%
\begin{subequations}
\begin{align}
 V^{\rm TI-2} &\equiv-\frac{V^{\rm ET1} V^{\rm HT2}}{E_3-E_1} -\frac{V^{\rm ET2} V^{\rm HT1}}{E_4-E_1}  \;,\\
 V^{\rm TI-3} &\equiv \frac{V^{\rm CT} \left( V^{\rm ET1} V^{\rm ET2} + V^{\rm HT1} V^{\rm HT2}\right) }{(E_3-E_1)(E_4-E_1)} \;.
\end{align}
\end{subequations}
%
However, 
the differences between the original Fujimoto's model and the newly derived OEP\hyp{}based model 
are: 
%
\begin{enumerate}
 \item The Hamiltonian matrix elements are evaluated from the fragment effective 
parameters, for which only the one\hyp{}electron integrals are needed. Therefore, the computational
cost is significantly reduced as compared to the parent TI/CIS model. In particular, 
$V^{\rm Coul}$ is evaluated by using the TrCAMM method developed previously,
$V^{\rm Exch}$ and $V^{\rm CT}$ are computed from the Mulliken approximated
formulae in Eqs. XXX, and XXX, as well as $V^{\rm ET1}$, $V^{\rm ET2}$,
$V^{\rm HT1}$ and $V^{\rm HT2}$ are treated by the generalized density fitting
with OEP effective matrices as effective parameters spanned in auxiliary AO basis set 
(Eqs.XXX); 
 \item The relaxation effects due to the intermolecular interactions are not included
in the current OEP\hyp{}based model.
Note that in the original TI/CIS model the basis states and all the one\hyp{}particle density matrices are built from the
self\hyp{}consistently adjusted fragment densities according to the DFI method.
\end{enumerate}
%
\paragraph*{Overlap corrections to the Hamiltonian.}
Since in the TI/CIS method the basis states are constructed from the monomer wavefunctions,
the overlap effects should be properly taken into account. It was reported previously
that overlap correction to the $\left< \Phi_1 \vert \mathscr{H} \vert \Phi_2 \right>$ 
matrix element brings negligible contributions to the 
total EET coupling (c.f. the `overlap' contribution in Ref.). On the other hand,
the importance of the overlap effects on the other off\hyp{}diagonal Hamiltonian matrix elements were not directly studied. 
After the overlap correction, the constituents of the direct coupling take the form
%
\begin{subequations}\label{e:ovrl-direct}
\begin{align}
 V^{\rm Coul} &= \frac{V^{{\rm Coul},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Exch} &= \frac{V^{{\rm Exch},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Ovrl} &=-\frac{(E_1+E_2)S_{12}}{2(1-S_{12}^2)}   \;.
\end{align}
\end{subequations}
%
The overlap\hyp{}corrected ET, HT and CT matrix elements read
%
\begin{equation}\label{e:ovrl-indirect}
 V^{\rm t} = \left[ 1 - S_{\rm t}^2 \right]^{-1} \left\{ V^{{\rm t},(0)} - \frac{1}{2} (E_1+E_2) S_{\rm t} \right\} \;,
\end{equation}
%
where `t' denotes one of the matrix element types (ET1, ET2, HT1, HT2, CT) 
and $S_{\rm t}$ is the appropriate overlap integral between basis states.
Since evaluation
of Eqs.~\eqref{e:ovrl-direct} and \eqref{e:ovrl-indirect} 
is computationally inexpensive, we shall consider the overlap\hyp{}corrected
Hamiltonian in the present work.

@@

As developed in Ref.\cite{Blasiak.Bednarska.Choluj.Bartkowiak.XXXX}, 
the matrix elements of the OEP operators
are computed from the generalized density fitting scheme, according to which
%
\begin{equation}
 V^X_{\xi, M} = \sum_{\xi'\in X}^{\rm DF} 
                \sum_{\varepsilon\in X}^{\rm RI}
                [{\bf R}^{-1}]_{\xi\xi'} R_{\xi'\varepsilon} H^X_{\varepsilon, M} \;,
\end{equation}
%
where
%
\begin{equation}
 H^X_{\varepsilon, M} = \sum_{\varepsilon'\in X}^{\rm RI}
                        [{\bf S}^{-1}]_{\varepsilon\varepsilon'} a_{\varepsilon'}^{X; M} \;.
\end{equation}
%
In the above equations, the auxiliary matrices are defined by
%
\begin{equation}
 S_{\eta\xi}  = \int 
                       \varphi^*_\eta({\bf r}) \varphi_\xi({\bf r}) 
                 d{\bf r} 
\end{equation}
%
and
%
\begin{equation}
 R_{\eta\xi}  = \iint 
                       \frac{ \varphi^*_\eta({\bf r}_1) \varphi_\xi({\bf r}_2) } 
                            {\vert {\bf r}_1 - {\bf r}_2\vert}  
                 d{\bf r}_1 d{\bf r}_2 \;.
\end{equation}
%
The elements of vector ${\bf a}^X$ for $M=$ ET1, ET2, HT1 and HT2 and $X=A, B$ are given by
%
\begin{subequations}
\begin{align}
a_{\alpha}^{A;{\rm ET1}} &= \sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^A_{\beta  H} C^A_{\gamma L} - C^A_{\beta  L} C^A_{\gamma H}\right\} C^A_{\delta H} \;,\\
%
a_{\alpha}^{B;{\rm ET1}} &= \sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \;,\\
%
a_{\alpha}^{B;{\rm ET2}} &= \sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^B_{\beta  H} C^B_{\gamma L} - C^B_{\beta  L} C^B_{\gamma H}\right\} C^B_{\delta H} \;,\\
%
a_{\alpha}^{A;{\rm ET2}} &= \sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \;,\\
%
a_{\alpha}^{A;{\rm HT1}} &=-\sum_\beta C_{\beta H}^A F_{\alpha\beta}^A \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^A_{\beta  L} C^A_{\gamma H} - C^A_{\beta  H} C^A_{\gamma L}\right\} C^A_{\delta L} \;,\\
%
a_{\alpha}^{B;{\rm HT1}} &=-\sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \;,\\
%
a_{\alpha}^{B;{\rm HT2}} &=-\sum_\beta C_{\beta H}^B F_{\alpha\beta}^B \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^B_{\beta  L} C^B_{\gamma H} - C^B_{\beta  H} C^B_{\gamma L}\right\} C^B_{\delta L} \;,\\
%
a_{\alpha}^{A;{\rm HT2}} &=-\sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \;.
\end{align}
\end{subequations}
%
% -----------------------
\bibliography{references}
% -----------------------

>>>>

\begin{multline}\label{e:v0-fujimoto}

@@

The first term in Eq.~\eqref{e:v0-fujimoto} is the, so called, `direct' coupling, which is 
composed of two contributions:
%
\begin{equation}
 \left< \Phi_1 \vert \mathscr{H} \vert \Phi_2 \right> = V^{{\rm Coul},(0)} + V^{{\rm Exch},(0)}
\end{equation}
%
where the F{\"o}rster (or Coulomb) coupling is given by
%
\begin{equation}
 V^{{\rm Coul},(0)} = \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
  P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
  \braket{\mu\nu}{\sigma\lambda}  \;,
\end{equation}
%
whereas the Dexter (or exchange) coupling is
%
\begin{equation}
 V^{{\rm Exch},(0)} =-\frac{1}{2} \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
  P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
  \braket{\mu\nu}{\sigma\lambda}  \;.
\end{equation}
%
In the above equations, ${\bf P}^{g\rightarrow e(X)}$ is the transition total one\hyp{}
particle density matrix of molecule $X$ in AO representation. $V^{{\rm Coul},(0)}$,
which is usually a leading term for singlet-singlet EET (but vanishes for triplet-triplet EET)
can be efficiently evaluated by various multipole expansion models published to date.
$V^{{\rm Exch},(0)}$ is known to be negligible, even for close intermolecular contacts.
However, unlike the direct coupling, the second and third term in Eq.~\eqref{e:v0-fujimoto}, which is collectively
referred to by Fujimoto as the `indirect' coupling, are not negligible at short intermolecular distances.
Unfortunately, evaluation of the indirect coupling is quite expensive and requires evaluation
of the electron repulsion integrals (ERI's).

%First, in Section II we briefly review the Fujimoto's TI/CIS model of EET coupling
%which is treated in this work as a reference.
%Then, further in this Section, we derive the OEP model based on the TI/CIS model (here referred to as the
%which is validated in Section III against the TI/CIS method for a few model complexes. 
Since the TI/CIS model was found very accurate to estimate EET coupling constants for many organic
molecules, we consider this model as a starting point to develop computationally more effcient
scheme that does not involve electron repulsion integrals at all.
First, in Section II we derive the OEP model based on the TI/CIS model (here referred to as the
OEP-TI/CIS model). Next, we validate it against the TI/CIS method for a few model complexes
in Section III. 
Finally, we conclude our work in Section IV.

@@

%In the above equatons, the superscript (0) denotes that the matrix elements are not affected by the
%overlap between molecular wavefunctions, and are given by
%%
% V^{{\rm CT },(0)} &= 
%     2 \big( H^A L^B \big| L^A H^B \big) - \big( H^A H^B \big| L^A L^B \Big) 
%\end{align}
%%

To account for the EET coupling via charge transfer states ...

@@

The Hamiltonian matrix element that is associated with the charge transfer process
is
%
\begin{equation}\label{e:v0-ct}
 V^{{\rm CT },(0)} = 
     2 \braket{\phi_H^A \phi_L^B}{\phi_L^A \phi_H^B}
      -\braket{\phi_H^A \phi_H^B}{\phi_L^A \phi_L^B}
\end{equation}
%
Since it involves ERI's of type $\braket{AB}{AB}$ OEP's cannot be directly defined here.
However, Mulliken approximation allows one to express ERI's in terms of the
overlap and Coulomb integrals, i.e.,
%
\begin{equation}
 \braket{ij}{kl} \approx \frac{1}{4} S_{ij}S_{kl}
 \left[ \braket{ii}{kk} + \braket{ii}{ll} + \braket{jj}{kk} + \braket{jj}{ll}\right] \;.
\end{equation}
%
Application of the above approximation to Eq.~\eqref{e:v0-ct} yields
%
\begin{multline}\label{e:v0-ct.mulliken}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B}\right] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_H^B \phi_H^B}\right]  \;,
\end{multline}
%
where 
%
\begin{equation} 
 r_{UW}^X \equiv \braket{\phi_U^X \phi_U^X}{\phi_W^X \phi_W^X} \;.
\end{equation}
%
First of all, note that $r_{HL}^A$ and $r_{HL}^B$ are just constant numbers
associated with the isolated monomers and 
independent on the molecular aggregate. Also, the remaining four ERI's
can be considered as Coulombic interactions between HOMO and LUMO orbitals
of unperturbed molecular wavefunctions.
Then, applying distributed multipole expansion and truncating it on the monopole
one finds that
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} \approx \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} \;,
\end{equation}
%
where the charge centroids of HOMO orbitals are given by
%
\begin{equation} 
 {\bf r}_H^X = \tbraket{\phi_H^X}{\hat{\bf r}}{\phi_H^X} \;.
\end{equation}
%
Note that, once occupied molecular orbitals are localized, the above approximation
should yield correct description. LUMO orbitals are usually not much localized.
Here, we use the distributed cumulative atomic charges to represent them, %cite CAMM paper
%
\begin{equation} 
 q^X_{x,L} =-\sum_{\alpha\in x} \sum_\beta S_{\alpha\beta} C_{\alpha L}^X C_{\beta L}^X
\end{equation}
%
and one can find that assuming this one obtains
%
\begin{equation} 
 \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B} 
 \approx \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At}
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \;.
\end{equation}
%
The two remaining ERI's can be then approximated as follows:
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
 \approx -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} \;,
\end{equation}
%
and similarly for the twin ERI. To summarize the derivation, the CT matrix element
is approximately given by
%
\begin{multline}\label{e:v0-ct.mulliken.working}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\ 
 + \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} 
 + \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At} 
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \Big] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\
 -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} 
 -\sum_{x\in A}^{\rm At}
 \frac{q_{x;L}^A}{\vert {\bf r}_H^B - {\bf r}_x \vert} \Big]\;.
\end{multline}
%

@@

Mulliken approximation can also be used to treat the pure exchange coupling (Eq.).
It is straightforward to show that
%
\begin{multline}\label{e:v0-exch-mulliken}
V^{{\rm Exch},(0)} \approx -\frac{1}{8} \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
 P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
 S_{\mu\lambda}  S_{\sigma\nu} \times \\
 \left[ \braket{\mu\mu}{\sigma\sigma} + \braket{\lambda\lambda}{\nu\nu} 
      + \braket{\mu\mu}{\nu\nu} + \braket{\lambda\lambda}{\sigma\sigma}\right] \;.
\end{multline}
%
However, ERI's that involve AO's in two different molecules can be safely neglected.
That leads to the following simplified expression:
%
\begin{multline}\label{e:v0-exch.mulliken.working}
V^{{\rm Exch},(0)} \approx 
  -\frac{1}{8} \Big\{ \sum_{\mu\nu\in A} P_{\nu\mu}^{g\rightarrow e(A)} G_{\mu\nu}^A
    [{\bf s}^{AB} {\bf P}^{g\rightarrow e(B)} {\bf s}^{BA} ]_{\mu\nu} \\
  + \sum_{\sigma\lambda\in B} P_{\lambda\sigma}^{g\rightarrow e(B)} G_{\lambda\sigma}^B
    [{\bf s}^{BA} {\bf P}^{g\rightarrow e(A)} {\bf s}^{AB} ]_{\sigma\lambda} 
  \Big\}
\end{multline}
%
with $G_{\mu\nu} \equiv \braket{\mu\mu}{\nu\nu}$. Note that $G_{\mu\nu}^A$ and $G_{\lambda\sigma}^B$
are just constant matrices that can be considered as effective fragment potentials.

@@

To summarize, the overall form of the OEP-TI/CIS model is still given as in the original TI/CIS model
by
%
\begin{equation}
  V \approx V^{\rm Direct} + V^{\rm Inirect} \;,
\end{equation}
%
where the so called `direct' and `indirect' coupling constants are respectively
%
\begin{subequations}
\begin{align}
  V^{\rm Direct  } &\equiv V^{\rm Coul} + V^{\rm Exch} + V^{\rm Ovrl} \;,\\
  V^{\rm Indirect} &\equiv V^{\rm TI-2} + V^{\rm TI-3} \;,
\end{align}
\end{subequations}
%
with
%
\begin{subequations}
\begin{align}
 V^{\rm TI-2} &\equiv-\frac{V^{\rm ET1} V^{\rm HT2}}{E_3-E_1} -\frac{V^{\rm ET2} V^{\rm HT1}}{E_4-E_1}  \;,\\
 V^{\rm TI-3} &\equiv \frac{V^{\rm CT} \left( V^{\rm ET1} V^{\rm ET2} + V^{\rm HT1} V^{\rm HT2}\right) }{(E_3-E_1)(E_4-E_1)} \;.
\end{align}
\end{subequations}
%
However, 
the differences between the original Fujimoto's model and the newly derived OEP\hyp{}based model 
are: 
%
\begin{enumerate}
 \item The Hamiltonian matrix elements are evaluated from the fragment effective 
parameters, for which only the one\hyp{}electron integrals are needed. Therefore, the computational
cost is significantly reduced as compared to the parent TI/CIS model. In particular, 
$V^{\rm Coul}$ is evaluated by using the TrCAMM method developed previously,
$V^{\rm Exch}$ and $V^{\rm CT}$ are computed from the Mulliken approximated
formulae in Eqs.~\eqref{e:v0-exch.mulliken.working}, and \eqref{e:v0-ct.mulliken.working}, respectively,
as well as $V^{\rm ET1}$, $V^{\rm ET2}$,
$V^{\rm HT1}$ and $V^{\rm HT2}$ are treated by the generalized density fitting
with OEP effective matrices as effective parameters spanned in auxiliary AO basis set 
(Eqs.~\eqref{e:v0-et1-oep}, \eqref{e:v0-et2-oep}, \eqref{e:v0-ht1-oep}, \eqref{e:v0-ht2-oep}
and Eqs.~\eqref{e:a:voep}-\eqref{e:a:aoep}); 
 \item The relaxation effects due to the intermolecular interactions are not included
in the current OEP\hyp{}based model.
Note that in the original TI/CIS model the basis states and all the one\hyp{}particle density matrices are built from the
self\hyp{}consistently adjusted fragment densities according to the DFI method.
\end{enumerate}
%
\paragraph*{Overlap corrections to the Hamiltonian.}
Since in the TI/CIS method the basis states are constructed from the monomer wavefunctions,
the overlap effects should be properly taken into account. It was reported previously
that overlap correction to the $\left< \Phi_1 \vert \mathscr{H} \vert \Phi_2 \right>$ 
matrix element brings negligible contributions to the 
total EET coupling (c.f. the `overlap' contribution in Ref.). On the other hand,
the importance of the overlap effects on the other off\hyp{}diagonal Hamiltonian matrix elements were not directly studied. 
After the overlap correction, the constituents of the direct coupling take the form
%
\begin{subequations}\label{e:ovrl-direct}
\begin{align}
 V^{\rm Coul} &= \frac{V^{{\rm Coul},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Exch} &= \frac{V^{{\rm Exch},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Ovrl} &=-\frac{(E_1+E_2)S_{12}}{2(1-S_{12}^2)}   \;.
\end{align}
\end{subequations}
%
The overlap\hyp{}corrected ET, HT and CT matrix elements read
%
\begin{equation}\label{e:ovrl-indirect}
 V^{\rm t} = \left[ 1 - S_{\rm t}^2 \right]^{-1} \left\{ V^{{\rm t},(0)} - \frac{1}{2} (E_1+E_2) S_{\rm t} \right\} \;,
\end{equation}
%
where `t' denotes one of the matrix element types (ET1, ET2, HT1, HT2, CT) 
and $S_{\rm t}$ is the appropriate overlap integral between basis states.
Since evaluation
of Eqs.~\eqref{e:ovrl-direct} and \eqref{e:ovrl-indirect} 
is computationally inexpensive, we shall consider the overlap\hyp{}corrected
Hamiltonian in the present work.

@@

As developed in Ref.\cite{Blasiak.Bednarska.Choluj.Bartkowiak.XXXX}, 
the matrix elements of the OEP operators
are computed from the generalized density fitting scheme, according to which
%
\begin{equation}\label{e:a:voep}
 V^X_{\xi, M} = \sum_{\xi'\in X}^{\rm DF} 
                \sum_{\varepsilon\in X}^{\rm RI}
                [{\bf R}^{-1}]_{\xi\xi'} R_{\xi'\varepsilon} H^X_{\varepsilon, M} \;,
\end{equation}
%
where
%
\begin{equation}
 H^X_{\varepsilon, M} = \sum_{\varepsilon'\in X}^{\rm RI}
                        [{\bf S}^{-1}]_{\varepsilon\varepsilon'} a_{\varepsilon'}^{X; M} \;.
\end{equation}
%
In the above equations, the auxiliary matrices are defined by
%
\begin{equation}
 S_{\eta\xi}  = \int 
                       \varphi^*_\eta({\bf r}) \varphi_\xi({\bf r}) 
                 d{\bf r} 
\end{equation}
%
and
%
\begin{equation}
 R_{\eta\xi}  = \iint 
                       \frac{ \varphi^*_\eta({\bf r}_1) \varphi_\xi({\bf r}_2) } 
                            {\vert {\bf r}_1 - {\bf r}_2\vert}  
                 d{\bf r}_1 d{\bf r}_2 \;.
\end{equation}
%
The elements of vector ${\bf a}^{X;M}$ for $M=$ ET1, ET2, HT1 and HT2 and $X=A, B$ are given by
%
\begin{subequations}\label{e:a:aoep}
\begin{align}
a_{\alpha}^{A;{\rm ET1}} &= \sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^A_{\beta  H} C^A_{\gamma L} - C^A_{\beta  L} C^A_{\gamma H}\right\} C^A_{\delta H} \;,\\
%
a_{\alpha}^{B;{\rm ET1}} &= \sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \;,\\
%
a_{\alpha}^{B;{\rm ET2}} &= \sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^B_{\beta  H} C^B_{\gamma L} - C^B_{\beta  L} C^B_{\gamma H}\right\} C^B_{\delta H} \;,\\
%
a_{\alpha}^{A;{\rm ET2}} &= \sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \;,\\
%
a_{\alpha}^{A;{\rm HT1}} &=-\sum_\beta C_{\beta H}^A F_{\alpha\beta}^A \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^A_{\beta  L} C^A_{\gamma H} - C^A_{\beta  H} C^A_{\gamma L}\right\} C^A_{\delta L} \;,\\
%
a_{\alpha}^{B;{\rm HT1}} &=-\sum_\beta C_{\beta L}^B F_{\alpha\beta}^B \;,\\
%
a_{\alpha}^{B;{\rm HT2}} &=-\sum_\beta C_{\beta H}^B F_{\alpha\beta}^B \nonumber \\
 &+\sum_{\beta\gamma\delta} \braket{\alpha\beta}{\gamma\delta}
 \left\{ 2C^B_{\beta  L} C^B_{\gamma H} - C^B_{\beta  H} C^B_{\gamma L}\right\} C^B_{\delta L} \;,\\
%
a_{\alpha}^{A;{\rm HT2}} &=-\sum_\beta C_{\beta L}^A F_{\alpha\beta}^A \;.
\end{align}
\end{subequations}
%
% -----------------------
\bibliography{references}
% -----------------------
